R Notebook

### 2019-05-22 ICS_Cleaning.Rmd
includes functional script for processing OG data

#Import the clinical enrollment data from the cleaned merged epi file
    QFT<- read.csv("/Applications/Old Computer/Epi Project/Data_clean/complete-kenya.csv")
#The studyIDs of coenrolled people are NK#_TRU# and we want just the NK# to match the lab notes
    QFT$StudyID<-tstrsplit(QFT$StudyID, "_")[[1]]
#trim the data set to only those study IDs in the lab notes and select the columns you want
    QFT<- dplyr::filter(QFT, StudyID %in% PBMC$StudyID)%>%
        dplyr::select(StudyID, age, sex, QFT, SchistosomaIntensity)

#Merge the two tables together and keep all observations since the yerkes donors won't be in the epi data
    DonorInfo<-merge(PBMC, QFT, by="StudyID", all = TRUE)
#The class of variables gets messed up in the merge so re-class them
    DonorInfo$Cells.Vial<-as.numeric(as.character(DonorInfo$Cells.Vial))
    DonorInfo$QFT<-as.numeric(as.character(DonorInfo$QFT))
#Match the variable names of the ICS data
    DonorInfo<-dplyr::rename(DonorInfo, Donor = StudyID)

#Manual Edits that may get deleted after Kenya script is finalized
    DonorInfo$TB[DonorInfo$Donor=="NK2183"]<-as.character("Healthy Control")
    DonorInfo$QFT[DonorInfo$Donor=="NK2323"]<-0.04
    DonorInfo$SM[DonorInfo$Donor=="NK2325"]<-as.character("Unknown")
```

```{r read in all flowjo data tables}
#change working directory to wherever the exported files are
setwd("/Applications/Old Computer/Day Lab/Flow-Data/exported/")
#find all the csv filenames in that directory and put them in a list
filenames =list.files(pattern="*.csv")
#for each name in that list, assign it to the output of read.csv of that name
#aka read in each file by it's name
for (i in 1:length(filenames)) 
    assign(filenames[i], read.csv(filenames[i]))
```
```{r source functions used in this script}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/ICS-cleaning-functions.R")
```

@@

l<-list(CD4_Counts.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_Positive.csv, CD4.csv, 
        CD8_Counts.csv, CD8_Cytokine.csv, GD_Counts.csv, GD_Cytokine.csv)
l<-lapply(l, function(x) clean_flowjo_output(x))
l<-lapply(l, function(x) splitter(x, "Sample", "_", one="Donor", two="TB", three="SM", four="Stim"))
l<-lapply(l, function(x) remove_samples(x))
l<-lapply(l, function(x) fix.names(x))
l<-lapply(l, function(x) class_change(x))

>>>>

#Import the clinical enrollment data from the cleaned merged epi file
    QFT<- read.csv("/Applications/Old Computer/Epi Project/Data_clean/complete-kenya-filledin.csv")
#The studyIDs of coenrolled people are NK#_TRU# and we want just the NK# to match the lab notes
    QFT$StudyID<-tstrsplit(QFT$StudyID, "_")[[1]]
#trim the data set to only those study IDs in the lab notes and select the columns you want
    QFT2<-dplyr::select(QFT, StudyID, age, sex, QFT, SchistosomaIntensity)%>%
        dplyr::filter(StudyID %in% PBMC$StudyID)

#Merge the two tables together and keep all observations since the yerkes donors won't be in the epi data
    DonorInfo<-merge(PBMC, QFT2, by="StudyID", all = TRUE)
#The class of variables gets messed up in the merge so re-class them
    DonorInfo$Cells.Vial<-as.numeric(as.character(DonorInfo$Cells.Vial))
    DonorInfo$QFT<-as.numeric(as.character(DonorInfo$QFT))
#Match the variable names of the ICS data
    DonorInfo<-dplyr::rename(DonorInfo, Donor = StudyID)
    DonorInfo$TB<-gsub("Active TB", "TB", DonorInfo$TB)
    DonorInfo$TB<-gsub("Healthy Control", "HC", DonorInfo$TB)
    DonorInfo$SM<-gsub("Negative", "X", DonorInfo$SM)
    DonorInfo$SM<-gsub("Schisto+", "SM", DonorInfo$SM)
    DonorInfo$SM<-gsub("\\+", "", DonorInfo$SM)

#Manual Edits that may get deleted after Kenya script is finalized
    DonorInfo$TB[DonorInfo$Donor=="NK2183"]<-as.character("HC")
    DonorInfo$QFT[DonorInfo$Donor=="NK2323"]<-0.04
    DonorInfo$SM[DonorInfo$Donor=="NK2325"]<-as.character("Unknown")
```

```{r read in all flowjo data tables}
#change working directory to wherever the exported files are
setwd("/Applications/Old Computer/Day Lab/Flow-Data/exported/")
#find all the csv filenames in that directory and put them in a list
filenames =list.files(pattern="*.csv")
#for each name in that list, assign it to the output of read.csv of that name
#aka read in each file by it's name
for (i in 1:length(filenames)) 
    assign(filenames[i], read.csv(filenames[i]))
```

```{r source functions used in this script}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/ICS-cleaning-functions.R")
```

@@

l<-list(CD4_Counts.csv, CD4_Cytokine.csv, CD4_MFI.csv, CD4_Positive.csv, CD4.csv, 
        CD8_Counts.csv, CD8_Cytokine.csv, GD_Counts.csv, GD_Cytokine.csv)
l<-lapply(l, function(x) clean_flowjo_output(x))
l<-lapply(l, function(x) splitter(x, "Sample", "_", one="Donor", two="TB", three="SM", four="Stim"))
l<-lapply(l, function(x) remove_samples(x))
l<-lapply(l, function(x) fix.names(x))
l<-lapply(l, function(x) class_change(x))
l<-lapply(l, function(x) changeTB(x))
